Graphical Abstract\\ Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor

### 2018-09-11 graph-abs/graph-abs.tex
minor final edits
closes #26

\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{graph_abs.pdf}
    \end{center}
    \label{fig:graph-abs}
\end{figure}

>>>>

\begin{figure}[htbp!]
    \begin{center}
        %\includegraphics[width=0.3\textwidth]{keff_rem_cases.png}
        \includegraphics[width=0.49\textwidth]{ser_zone_II.png}
        \includegraphics[width=0.49\textwidth]{spectrum_zones.png}
    \end{center}
    \label{fig:graph-abs}
    \caption{The Molten Salt Breeder Reactor (left) was modeled in full
three-dimensional detail.  Yellow represents fuel salt, purple represents
graphite, and aqua represents the reactor vessel Online liquid fuel processing
was simulated until a quasi-equillibrium of fuel composiion could be
established. Reactor physics parameters, such as flux profiles, were evaluated
during the 10 year evolution.}
\end{figure}
